ext_risk_copula

### 2019-02-20 ext_risk_copula.Rmd
bug fixed

qrng<-runif(10000,min=0,max=r_bf_hassell)
qr<-quantile(qrng,probs=c(.025,.975))

@@

pdf("./Results/hassell/hassell_extrisk_d0.pdf",height = 6,width=6)
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = c(1.4,7.6),
     xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted")

@@

qrng<-runif(10000,min=0,max=r_bf_msmith)
qr<-quantile(qrng,probs=c(.025,.975))

>>>>

qrng<-runif(10000,min=1,max=r_bf_hassell) # r must be > 1
qr<-quantile(qrng,probs=c(.025,.975))

@@

pdf("./Results/hassell/hassell_extrisk_d0.pdf",height = 6,width=6)
plot(hassell_extrisk_d0$r,hassell_extrisk_d0$risk_left_d0,col="red",type="b",ylim=c(0,1),xlim = range(rlist),
     xlab="r",ylab="Extinction risk",cex.lab=1.5,pch=1)
arrows(x0=hassell_extrisk_d0$r,y0=hassell_extrisk_d0$CI0.025left,
       x1=hassell_extrisk_d0$r,y1=hassell_extrisk_d0$CI0.975left,angle=90,length=0.1,col="red",code=3)
abline(v=rc_hassell,lty="dotted")

@@

qrng<-runif(10000,min=1,max=r_bf_msmith) #r must be > 1 for +ve eqm pt.
qr<-quantile(qrng,probs=c(.025,.975))
